---
title: "<div class='mytitle'>Pretty Markdown Template</div>"
author: "<div class='mysubtitle'>Chris Hoehne, PhD</div>"
date: "<div class='mysubtitle'>`r format(Sys.Date(), '%A, %B %d %Y')`</div>"
output: 
  html_document:
    css: ./style/style.css
    number_sections: TRUE
    toc: TRUE
    toc_float:
      collapsed: FALSE
    includes: 
      before_body: ./style/header.html
      after_body: ./style/footer.html
---

---

## Table of Contents {.toc}

[1 About](#intro)

[2 Data](#data)

[3 Visual](#visual)

[4 References](#references)

[5 Session](#session)

&nbsp;

---

# <a name="about"></a>About

Tell us about what you are doing here.

```{r setup, include = F, warning = F, message = F}

# custom functions & schemes
if(!require("here")){install.packages("here")} # first get here, easy file paths
if(file.exists(here::here("scripts/utils.R"))){ # if our utility script exists
  source(here::here("scripts/utils.R"))  # import
  } else { # but if it doesn't
    if(!require("devtools")){install.packages("devtools")} # source it from github with devtools
    devtools::source_url("https://github.com/cghoehne/templates/raw/main/scripts/utils.R")
    }

# load packages, installing any if needed, using the ipak utility function
packages <- c("DT", "ggplot2", "data.table", "here")
ipak(packages) # loads all packages, installing if needed

```



# <a name="data"></a>Data

A section overviewing the data, perhaps? Here we just are viewing the first 1,000 rows of `ggplot2::diamonds` with package `DT`.

&nbsp;

```{r datatable, warning = F, message = F, echo = F}

# just print the first 1k rows
datatable(head(diamonds, 1e3))

```



# <a name="visual"></a>Visual

Time to shine! Here are some sample figures.

&nbsp;

```{r Fig-1, eval = T, echo = F, warning = F, message = F, fig.dim = c(8, 4.5), fig.align = 'center', fig.cap = "<div class='figcap'><b>Fig 1.</b> A fancy hex plot.</div>" }

# sample plot with diamonds (my fancy hex plots)
source(here("scripts/hex-plot.R"))

hex.plot

```

&nbsp;

```{r Fig-2, eval = T, echo = F, warning = F, message = F, fig.dim = c(8, 4.5), fig.align = 'center', fig.cap = "<div class='figcap'><b>Fig 1.</b> Another fancy hex plot. This one has a log10 x & y scales with R^2 and p-value for a simple linear model.</div>" }

hex.log.lm.plot

```

# <a name="references"></a>References

&nbsp;

1. Hoehne, Christopher. (2020). https://github.com/cghoehne.

2. Holtz, Yan. (2018). "Pimp my RMD: a few tips for R Markdown." https://holtzy.github.io/Pimp-my-rmd/.

&nbsp;
&nbsp;
&nbsp;
&nbsp;

<div class='myfootnote'>NOTE: you should cite your packages and R here, I just haven't yet (but see below for session details).</div>

#  <a name="session"></a>Session

&nbsp;

```{r session}

sessionInfo()

```

&nbsp;
&nbsp;
&nbsp;
&nbsp;