---
title: "<div class='mytitle'>Pretty Markdown Template</div>"
author: "<div class='mysubtitle'>Chris Hoehne, PhD</div>"
date: "<div class='mysubtitle'>`r format(Sys.Date(), '%A, %B %d %Y')`</div>"
output: 
  html_document:
    css: ./style/style.css
    number_sections: TRUE
    toc: TRUE
    toc_float:
      collapsed: FALSE
    includes: 
      before_body: ./style/header.html
      after_body: ./style/footer.html
---

<!------(header here)------->

---

## Table of Contents {.toc}

[1 About](#intro)

[2 Data](#data)

[3 Visual](#visual)

[4 References](#references)

[5 Session](#session)

&nbsp;

---

<!----------(\)----------->

# <a name="about"></a>About

Tell us about what you are doing here.

```{r setup, include = F, warning = F, message = F}

set.seed(42)

# source utilities script
my.util.path <- here::here("scripts/utils.R")
if(!require("here")){install.packages("here")}
if(!file.exists(my.util.path)){
  download.file("https://github.com/cghoehne/templates/raw/main/scripts/utils.R", 
                destfile = my.util.path) }
source(my.util.path)

# load packages, installing any if needed, using the ipak utility function
packages <- c("showtext", "DT", "ggplot2", "data.table", "here")
ipak(packages) # loads all packages, installing if needed. from above utils

# fonts
# font_paths()
#font_files()
# https://fonts.google.com/featured/Superfamilies
#font_add_google("Montserrat", "Montserrat")

# syntax: font_add(family = "<family_name>", regular = "/path/to/font/file")
font_add("Palatino", "pala.ttf")
#font_families()
my.font <- "Palatino"

# automatically use showtext for new devices
showtext_auto() 

# indices for table/figure counting
table.n <- 1L
fig.n <- 1L # FIXME not using

```

<!-------------->

# <a name="data"></a>Data

A section overviewing the data, perhaps? Here we just are viewing the first 1,000 rows of `ggplot2::diamonds` with package `DT`.

&nbsp;

<div class='figcap'><b>Table `r paste0(table.n)`. </b>Diamond data.</div>

```{r datatable, warning = F, message = F, echo = F}

datatable(head(diamonds, 1e3), # just print the first 1k rows
          extensions = 'FixedColumns', filter = 'top',
          options = list(
            dom = 'tfp', # order matters; t = table, f = filter, p = pagination
            scrollX = TRUE,
            scrollCollapse = TRUE) )

table.n <- table.n + 1L

```

<!-------------->

# <a name="visual"></a>Visual

Time to shine! Here are some sample figures.

&nbsp;

```{r hex-plot, eval = T, echo = F, warning = F, message = F, fig.dim = c(8, 4.5), fig.align = 'center', fig.cap = paste0("<div class='figcap'><b>Fig ", fig.n, ".</b> A fancy hex plot.</div>") }

# sample plot with diamonds (my fancy hex plots)
source(here("scripts/hex-plot.R"))

# factor to scale for markdown output
fs <- 3 # FIXME why does text display resolution mismatch between .Rmd and .html

hex.plot +
  theme(title = element_text(color = "black", family = my.font),
        plot.title = element_text(size = 10*fs, color = "black", family = my.font),
        text = element_text(color = "black", family = my.font),
        legend.title = element_text(size = 9*fs, color = "black", family = my.font),
        legend.text = element_text(size = 9*fs, color = "black", family = my.font),
        axis.text = element_text(color = "black", family = my.font),
        axis.title.x = element_text(margin = margin(t = 2, r = 0, b = 1, l = 0), 
                                    color = "black", family = my.font, size = 10*fs),
        axis.title.y = element_text(margin = margin(t = 0, r = 2, b = 0, l = 1), 
                                    color = "black", family = my.font, size = 10*fs),
        axis.text.x = element_text(margin = margin(t = 1, r = 0, b = 1, l = 0, "mm"),
                                   color = "black", family = my.font, size = 9*fs),
        axis.text.y = element_text(margin = margin(t = 0, r = 1, b = 0, l = 1, "mm"),
                                   color = "black",family = my.font, size = 9*fs),
        axis.line.x = element_line(size = 0.5, linetype = "solid", colour = "black"),
        axis.line.y = element_line(size = 0.5, linetype = "solid", colour = "black"))

```

```{r, echo = F, message = F, warning = F}
fig.n <- fig.n + 1
```

&nbsp;

```{r log-hex-plot, eval = T, echo = F, warning = F, message = F, fig.dim = c(8, 4.5), fig.align = 'center', fig.cap = paste0("<div class='figcap'><b>Fig ", fig.n, ".</b> Another fancy hex plot. This one has a log<sub>10</sub> x & y scales with R<sup>2</sup> and p-value for a simple linear model.</div>") }

hex.log.plot +
  theme(title = element_text(color = "black", family = my.font),
        plot.title = element_text(size = 10*fs, color = "black", family = my.font),
        text = element_text(color = "black", family = my.font),
        legend.title = element_text(size = 9*fs, color = "black", family = my.font),
        legend.text = element_text(size = 9*fs, color = "black", family = my.font),
        axis.text = element_text(color = "black", family = my.font),
        axis.title.x = element_text(margin = margin(t = 2, r = 0, b = 1, l = 0), 
                                    color = "black", family = my.font, size = 10*fs),
        axis.title.y = element_text(margin = margin(t = 0, r = 2, b = 0, l = 1), 
                                    color = "black", family = my.font, size = 10*fs),
        axis.text.x = element_text(margin = margin(t = 3.5, r = 0, b = 1, l = 0, "mm"),
                                   color = "black", family = my.font, size = 9*fs),
        axis.text.y = element_text(margin = margin(t = 0, r = 3.5, b = 0, l = 1, "mm"),
                                   color = "black",family = my.font, size = 9*fs),
        axis.line.x = element_line(size = 0.5, linetype = "solid", colour = "black"),
        axis.line.y = element_line(size = 0.5, linetype = "solid", colour = "black")) +
  
  # see scripts/hex-plot for the raw
  # TODO integrate the scaling factor for text in hex-plot.R, could even do different sizings/headings
  annotate("text", y = a.yr, x = a.xr, label = bquote(R^2 == .(r2.dt)), size = 3*fs, family = my.font) +
  annotate("text", y = a.yp, x = a.xp, label = bquote(italic(.(pval.lab.dt))), size = 3*fs, family = my.font)

```

```{r, echo = F, message = F, warning = F}

fig.n <- fig.n + 1

```

# <a name="references"></a>References

&nbsp;

1. Hoehne, Christopher. (2020). https://github.com/cghoehne.

2. Holtz, Yan. (2018). "Pimp my RMD: a few tips for R Markdown." https://holtzy.github.io/Pimp-my-rmd/.

<!-------------->

&nbsp;
&nbsp;
&nbsp;
&nbsp;

<div class='myfootnote'>**foot*****NOTE***: if you are using this more formarlly, you should probably cite your packages, R (i.e. `utils::citation()`), etc. Instead, I just include the session and package details below).</div>

<!-------------->

# <a name="session"></a>Session & Packages

&nbsp;
&nbsp;

<div class='figcap'><b>Table `r paste0(table.n)`. </b>R environment session info for reproducibility of results.</div>

```{r session-table, echo = F, message = F, warning = F, fig.align = "center", out.width = '100%', results = 'asis'}

invisible(ipak("devtools"))

session.platform <- data.frame(cbind(names(unlist(devtools::session_info()$platform)), 
                                     unlist(devtools::session_info()$platform)), row.names = NULL)

colnames(session.platform) <- c("Setting", "Value")

knitr::kable(
  session.platform, 
  booktabs = T, 
  align = "l",
  caption.short = " "
  )

table.n <- table.n + 1L

```

&nbsp;
&nbsp;
&nbsp;

<div class='figcap'><b>Table `r paste0(table.n)`. </b>Package info for reproducibility of results.</div>

```{r package-table, echo = F, message = F, warning = F, fig.align = "center", out.width = '100%', results = 'asis'}

session.packages <- as.data.frame(devtools::session_info()$packages)
attached.packages <- session.packages[session.packages$attached == T, 
                                      c("package", "loadedversion", "date")]

colnames(attached.packages) <- c("Package", "Loaded version", "Date")
rownames(attached.packages) <- NULL

knitr::kable(
  attached.packages, 
  booktabs = T, 
  align = "l",
  caption.short = " ")

table.n <- table.n + 1L

```

&nbsp;
&nbsp;
&nbsp;
&nbsp;

<!------(footer here)------->